Abstract Binding Trees

### 2015-10-26 paper.tex
Fix up font reference
Use microtype package
Adjust spacing for arities
Sort packages
Disable xelatex-specific package
Enable linux libertine font
Add some references (#5)
Add a couple of citations

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath, amsthm, stmaryrd, scalerel, amssymb}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{ifthen}
\usepackage{proof}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{xltxtra}
\usepackage{xunicode}

@@

% fonts
% \setromanfont[Mapping=tex-text, Ligatures=Rare, Numbers=OldStyle]{Linux Libertine O}
\setmathfont{Asana-Math.otf}

@@

\newcommand\MkValence[3]{%
  \ifthenelse{\equal{#1}{}}{}{%
    \{#1\}%
  }%
  \ifthenelse{\equal{#2}{}}{}{%
    [#2]%
  }.\, #3
}
\newcommand\MkBTm[3]{\{#1\}[#2].\, #3}
\newcommand\MkArity[2]{(#1) #2}
\newcommand\IsArity[1]{\IMode{#1}\ \textit{arity}}
\newcommand\IsValence[1]{\IMode{#1}\ \textit{valence}}
\newcommand\IsSort[1]{\IMode{#1}\ \textit{sort}}
\newcommand\Leq[2]{\IMode{#1}\leq\IMode{#2}}

@@

Crary has demonstrated a first-order encoding of contexts in the logical
framework in bijection with actual LF-contexts, which has been successfully
used in large-scale mechanization efforts, including that of Standard ML and
the Edinburgh Logical Framework itself.

%%% TODO: Cite Crary; cite mechaniziation of Standard ML; cite Martens & Crary
%%% TODO: talk about context encodings in Abella

@@

>>>>

\usepackage[usenames,dvipsnames,svgnames,table]{xcolor}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{fontspec}
\usepackage{geometry}
\usepackage{graphicx}
\usepackage{ifthen}
\usepackage{mathtools}
\usepackage{proof}
\usepackage{scalerel}
\usepackage{stmaryrd}
\usepackage{supertabular}
\usepackage{tikz-cd}
\usepackage{unicode-math}
\usepackage{xunicode}

@@

% fonts
\usepackage[
  activate={true,nocompatibility},
  final,
  tracking=true
]{microtype}
\setmainfont{Linux Libertine O}
\setmathfont{Asana Math}

@@

\newcommand\MkValence[3]{%
  \ifthenelse{\equal{#1}{}}{}{%
    \{#1\}%
  }%
  \ifthenelse{\equal{#2}{}}{}{%
    [#2]%
  }.\, #3
}
\newcommand\MkBTm[3]{\{#1\}[#2].\, #3}
\newcommand\MkArity[2]{(#1)\, #2}
\newcommand\IsArity[1]{\IMode{#1}\ \textit{arity}}
\newcommand\IsValence[1]{\IMode{#1}\ \textit{valence}}
\newcommand\IsSort[1]{\IMode{#1}\ \textit{sort}}
\newcommand\Leq[2]{\IMode{#1}\leq\IMode{#2}}

@@

Crary has demonstrated a first-order encoding of contexts in the logical
framework in bijection with actual LF-contexts \cite{crary:2009}, which has
been successfully used in large-scale mechanization efforts, including that of
Standard ML \cite{lee-crary-harper:2007} and the Edinburgh Logical Framework
itself \cite{martens-crary:2012}.

%%% TODO: talk about context encodings in Abella

@@

\nocite{*}
\bibliographystyle{abbrv}
\bibliography{refs}
